\documentclass[12pt]{article}
\usepackage[hmargin=0.5in, vmargin=0.25in, includeheadfoot]{geometry}
\usepackage{amsmath, amsthm, booktabs}
%\usepackage{fancyheadings}
%\usepackage{hyperref}


%\pagestyle{fancy}

\newcommand{\Cov}{\mathrm{Cov}}
\newcommand{\Var}{\mathrm{Var}}
\newcommand{\Beta}{\mathrm{Beta\,}}


\begin{document}
%\maketitle

\begin{center}
  {\Large\bf Evaluation of Final Presentations\\[1ex]
    STAT 5255 Introduction to Data Science, Fall 2021}
\end{center}

\begin{center}
\begin{tabular}{|lr|}
\hline
& \\
{\Large Evaluator's Name:} \hfill & \phantom{xxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxx} \\
& \\
\hline
\end{tabular}
\end{center}

\vspace{2cm}


Please evaluate each presenter based on the following three aspects.

\begin{itemize}
\item 
Domain:
Does the presentation show adequate motivation for this work? 
Does it tell us what this project is for and why it will matter?
Are existing works properly reviewed?

\item
Methods:
Are the variables meaningfully constructed?
Are the methods appropriate to the problem? 
How well was the method adapted to the application? 
Are the computational methods used appropriately?
Are potential limitations acknowledged?

\item
Presentation:
Is the presentation clear, professional, and informative
to the general audience?
How well are the findings interpreted in a non-technical way?
Are the tables and figures conveying what they should do?
\end{itemize}

\vspace{2cm}

On a 5 to 1 scale (5 means excellent and 1 means poor), please
circle your evaluation for each presenter.

\begin{center}
\begin{tabular}{cccc}
\toprule
Presenter & Domain & Methods & Presentation\\
\midrule \\
 & \phantom{xxx}5 4 3 2 1 \phantom{xxx} & \phantom{xxx}5 4 3 2 1 \phantom{xxx} & \phantom{xxx} 5 4 3 2 1 \phantom{xxx} \\\\
 & \phantom{xxx}5 4 3 2 1 \phantom{xxx} & \phantom{xxx}5 4 3 2 1 \phantom{xxx} & \phantom{xxx} 5 4 3 2 1 \phantom{xxx} \\\\
 & \phantom{xxx}5 4 3 2 1 \phantom{xxx} & \phantom{xxx}5 4 3 2 1 \phantom{xxx} & \phantom{xxx} 5 4 3 2 1 \phantom{xxx} \\\\
 & \phantom{xxx}5 4 3 2 1 \phantom{xxx} & \phantom{xxx}5 4 3 2 1 \phantom{xxx} & \phantom{xxx} 5 4 3 2 1 \phantom{xxx} \\\\
\bottomrule
\end{tabular}
\end{center}

\end{document}
